Develop atlantisom wrappers

### 2020-01-17 WrapperDevelopment.Rmd
rearranging functions for survey setup

@@

om_index <- function(surveyconfig = survey_configfile, 
                     fisheryconfig = fishery_configfile, 
                     omlist_ss = omlist_ss, 
                     n_reps = n_reps,
                     save = TRUE){

  #configure the independent survey, a default census is in config/survcensus.R
  #survey configuration must specify survey time, area, efficiency (q), selectivity
  #survey species inherited from omlist_ss
  source(surveyconfig)

  #biomass based fishery independent survey index
  # this uses result$biomass_ages to sample biomass directly, no need for wt@age est
  survey_B <- atlantisom::create_survey(dat = omlist_ss$truebio_ss,
                                        time = survtime,
                                        species = survspp,
                                        boxes = survboxes,
                                        effic = surveffic,
                                        selex = survselex)

@@

}

@@

CC3om_sard_ind <- om_index(surveyconfig = here("config/survcensus.R"), 
                           fisheryconfig = "",
                           omlist_ss = CC3om_sardine, 
                           n_reps = 5, 
                           save = FALSE)

>>>>

```{r surveyconfig}

surveyconfig <- function(omlist_ss, usersurvey = usersurvey_file){
  #configure the independent survey, a default census is in config/survcensus.R
  #survey configuration must specify survey time, area, efficiency (q), selectivity
  #survey species inherited from omlist_ss
  survspp <- omlist_ss$species_ss
  # survey season and other time dimensioning parameters
  # generalized timesteps all models
  noutsteps <- omlist_ss$runpar$tstop/omlist_ss$runpar$outputstep
  timeall <- c(0:noutsteps)
  stepperyr <- if(omlist_ss$runpar$outputstepunit=="days") 365/omlist_ss$runpar$toutinc
  midptyr <- round(median(seq(0,stepperyr)))

  # model areas, subset in surveyconfig
  allboxes <- c(0:(omlist_ss$boxpars$nbox - 1))

  # fishery output: learned the hard way this can be different from ecosystem outputs
  fstepperyr <- if(omlist_ss$runpar$outputstepunit=="days") 365/omlist_ss$runpar$toutfinc

  # survey selectivity (agecl based)
  # should return all age classes fully sampled (Atlantis output is 10 age groups per spp)
  n_age_classes <- omlist_ss$funct.group_ss$NumCohorts
  age_classes <- 1:n_age_classes

  n_annages <- n_age_classes * omlist_ss$funct.group_ss$NumAgeClassSize
  annages <- 1:n_annages

  # user options for survey--default is a census with mid-year sample
  source(usersurvey, local = TRUE)

  surveyspecs <- list("survtime" = survtime,
                      "survboxes" = survboxes,
                      "surveffic" = surveffic,
                      "survselex" = survselex,
                      "surveffN" = surveffN,
                      "surv_cv" = surv_cv)

  return(surveyspecs)
}
```

```{r specsex}

mysurvey <- surveyconfig(CC3om_sardine, here("config/usersurvey.R"))
```

@@

om_index <- function(usersurvey = usersurvey_file, 
                     userfishery = userfishery_file, 
                     omlist_ss, 
                     n_reps = n_reps,
                     save = TRUE){

  surveyspec <- surveyconfig(omlist_ss, usersurvey = usersurvey_file)

  #biomass based fishery independent survey index
  # this uses result$biomass_ages to sample biomass directly, no need for wt@age est
  survey_B <- atlantisom::create_survey(dat = omlist_ss$truebio_ss,
                                        time = surveyspec$survtime,
                                        species = surveyspec$survspp,
                                        boxes = surveyspec$survboxes,
                                        effic = surveyspec$surveffic,
                                        selex = surveyspec$survselex)

@@

  #we are not currently subsetting fishery catch because we cannot correct catch.nc
  #  instead the catch in biomass from catch.txt is read in for the index
  #  we do not apply any cv to this, but we could this way (default cv=0)

  fishObsCatchB <- list()
  for(i in 1:n_reps){
    fishObsCatchB[[i]] <- atlantisom::sample_fishery_totcatch(omlist_ss$truecatchbio_ss, fish_cv)
  }

  if(save){
    saveRDS(fishObsCatchB, file.path(d.name, paste0(scenario.name, "fishCatch.rds")))
  }

  indices <- list("survObsBiomB" = survObsBiomB,
                  "fishObsCatchB" = fishObsCatchB)

  return(indices)
}

@@

CC3om_sard_ind <- om_index(surveyconfig = here("config/survcensus.R"), 
                           fisheryconfig = here("config/fisherycensus.R"),
                           omlist_ss = CC3om_sardine, 
                           n_reps = 5, 
                           save = FALSE)
